### 2019-08-09 README.Rmd
Update README layout

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
ggplot2::ggsave(
          "man/figures/rob2trafficlight.png",
          plot = trafficlight_rob,
          device = "png",
          width = 6,
          height = 9,
          units = "in",
          dpi = 800, 
          limitsize = FALSE)
```
<center><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></center>

>>>>

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
ggplot2::ggsave(
          "man/figures/rob2trafficlight.png",
          plot = trafficlight_rob,
          device = "png",
          width = 6,
          height = 9,
          units = "in",
          dpi = 800, 
          limitsize = FALSE)
```
<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>
